%\section{User-Contributed Intervention Ideas}
\chapter{User Feedback on GitHub Issues}
\label{ch:github}

Here is a complete list of feedback that users left us via the feedback interfaces in HabitLab, where users agreed to be have them be publicly shared on GitHub Issues. We removed all examples with any identifying information. Many of these are associated with images and screenshots, which can be viewed by clicking the GitHub link.

\begin{lstlisting}[breaklines]
https://github.com/habitlab/habitlab/issues/641
Hi - I love your app, but I have a few suggestions / requests.



I think it would be great if there was the option for greater control to select multiple nudges to function every time. In my scenario, the website I want to control is Youtube. I use Youtube a lot whilst I'm working and being productive for various tutorials, downloading copyright fee assets and so on. However, the recommended videos often push click bait "trending" content at me, and having gone on Youtube to find a tutorial on solving a certain problem, you suddenly find your self 5 minutes into a "You won't BELIEVE what Gordan Ramsey says to this Chef" or similar rubbish. I'd really like to be able to use the Feed Diet, Sidekicker, Supervisor, and No Comment at the same time. I feel like your app has everything I need, but I can't use it all at the same time :) 



Best,

Ben

https://github.com/habitlab/habitlab/issues/639
The disabling of autoplay makes me skip the recap of Jane The Virgin. However, that series includes new information and new jokes in every recap, so I always watch each recap even if I've just seen the previous episode. With autoplay on I can't watch the recap even if I've just logged in to Netflix, and even if I'm "rewinding" back to the beginning of the episode each time. It skips it again.

https://github.com/habitlab/habitlab/issues/638
it keeps asking me "how much do you want me to bother you??" and i am tired of answering this question. very cool extension that i used for like a year but something seems to have gone wrong so now i'm uninstalling :(

https://github.com/habitlab/habitlab/issues/637
I really wish there was a setting where I could use a nudge on every website except what's on a whitelist, because I always find a new place to waste time.

https://github.com/habitlab/habitlab/issues/635
Is there a way to set a default level of "how aggressive" for sites we want to reduce time on instead of choosing each time we load the site? ie, if I'm in the process of pulling up facebook, I'm much less likely to choose "heavy-handed" etc in the moment than I might in a more clear-headed moment ahead of time

https://github.com/habitlab/habitlab/issues/634
Disabling HabitLab due to excessive CPU usage. Right now the Chrome browser's TaskManage, CPU usage column shows HabitLab using 10-15% CPU. Ouch! Adios!

https://github.com/habitlab/habitlab/issues/633
What about separating out Amazon from it's Kindle page (read.amazon.com) and it music page (music.amazon.com) because I enjoy listening to music when I type, and (sometimes) I read books on my Kindle from the website for work.

https://github.com/habitlab/habitlab/issues/632
You should be able to group sites and provide overall limits and timers across the category. For instance, Netflix and YouTube would be considered 'media streaming' allowing the user to set a goal of say an hour of streaming a day. Otherwise, I can personally see me spreading my viewing over multiple different websites to (pretend to) keep within the goals.

https://github.com/habitlab/habitlab/issues/631
It's annoying that it asks always what nudge I want, when you open a website. Please stop this!

https://github.com/habitlab/habitlab/issues/629
It's annoying that it asks always what nudge I want, when you open a website. Please stop this!

https://github.com/habitlab/habitlab/issues/628
I have told this app again and again that I want to turn off 2 nudges, freeze scrolling, and setting the number of minutes I want to spend on a website in advance. HOWEVER IT KEEPS COMING BACK and I am almost about to delete this despite loving ever other aspect of it. FIX THAT ASAP. OR don't say you can remove it if you can't.

https://github.com/habitlab/habitlab/issues/627
Hey! Would be nice to have displayed the total amount of time spent on the web. Great work, people! Thank you for making this :)

https://github.com/habitlab/habitlab/issues/624
When I click sign in to sync nothing happens. I closed and opened new tabs and such and its still not working so I can't sign in

https://github.com/habitlab/habitlab/issues/620
Youtube nudges not working as expected. Sidebar and comments turned on and showing normally. How many nudges can I active simultaneuosly?

https://github.com/habitlab/habitlab/issues/618
I want to see my history and detailed results for longer durations, such as weeks or months

https://github.com/habitlab/habitlab/issues/617
I came to Facebook to check notifications for events, but the scroll freezer hides the entire top bar. And the search bar too! I can't manage the events that I came here to manage. The other HabitLab stuff is good though!

https://github.com/habitlab/habitlab/issues/616
Love HabitLab so far! However, I am unable to log in on the extension. I press the button and it does nothing.

https://github.com/habitlab/habitlab/issues/615
Thank you so much. I downloaded this to track my work time ( work on social media) and stumbled across the feed diet during one of the random cycles on youtube. I have never felt my mind clear like that just by not having the feed!! amazing extension, the possibilities are

https://github.com/habitlab/habitlab/issues/613
Nudges should NOT cover the page, they should possibly push the whole page down by the amount of space needed by the nudge: 

most apps, like twitter and facebook, have their buttons at the top, and your nudges simply cover those and make the site unusable, so maybe one wants to do a quick action on the sites bar and leave, but the nudge bar is in the way, so one is forced to close the nudge to access the function of the site and get on with it. But then the nudge is closed

Another possible solution is give the option to hide the nudge for 5-10 seconds instead of 1hour, but I prefer to see how the behaviour changes if the site usability is unencumbered



Mission Goal Nudges should allow at least to see what the page you were opening was. The objective can't be defined if you have multiple tabs open and you can't interpret from the url what the content you wanted to open was. Ideally it will be as blocking as it is now...so that it is the only action you can do, but you should be able to see the background page through for instance a darker screen, or a "peek" button that hides the nudge on rollover and shows it again as soon as you exit the button.

https://github.com/habitlab/habitlab/issues/610
ნიკა

https://github.com/habitlab/habitlab/issues/607
Show total browsing time including those pages not in top 5.

https://github.com/habitlab/habitlab/issues/606
Password for settings page, and nudge turn off buttons.

https://github.com/habitlab/habitlab/issues/605
Option to hide „Turn off HabitLab” button.

https://github.com/habitlab/habitlab/issues/604
Please add an option in settings to hide nudge turn off buttons (so they can only be turned off from settings page).

https://github.com/habitlab/habitlab/issues/601
On sites like news.google.com and reddit.com, you can click on links that take you to long articles on other domains where you can spend a significant chunk of time. Habit Lab doesn't track such changes now but really should!

https://github.com/habitlab/habitlab/issues/597
I want to see results per week and month - and to be able to compare each week / month. Also, an option to choose which day the week starts

https://github.com/habitlab/habitlab/issues/594
My nudges are not working most of time.

https://github.com/habitlab/habitlab/issues/593
i would like to suggest maybe you can make another tracking nudge that only allows you to stay on a certain website and cant open any other tabs

https://github.com/habitlab/habitlab/issues/590
Hi there, 



Sometimes, habit lab seems to turn off and I have no idea why. I haven't seen any nudges on facebook in the past week, but I didn't change any of my settings. This is the second time I've had this issue (last time I had to reinstall habit lab to fix it). What's the best way to fix this?

https://github.com/habitlab/habitlab/issues/589
Add minutes, not percentages, so i can see how many minutes i wasted on certain sites!

https://github.com/habitlab/habitlab/issues/587
Banner says a different website than the one I'm actually on.

https://github.com/habitlab/habitlab/issues/585
It won't show nudges

https://github.com/habitlab/habitlab/issues/583
In general, I think the random is a good idea, but I quickly realize some of the random ones are ineffective for me. Rather than the random, it would be great if I could designate 1 feature for a particular website. For example, I know that facebook is a big time waster to me and moreso than others. I would love it if that was 1 one minute kick-off no matter what. Others (eg - Twitter) are less of a distraction for me, so the random wouldn't be as painful.

https://github.com/habitlab/habitlab/issues/577
For the past few days, it only seems to track YouTube for some reason. Is there a way I could fix this?

https://github.com/habitlab/habitlab/issues/576
Hello! I am not sure if I am understanding properly, but with the Bouncer nudge (my favourite), once you have done it once in a day it never triggers again. It would be good for it to ask every time I go to a site, how long I want to spend on it. And if I exit the site, it refreshes and starts again.

https://github.com/habitlab/habitlab/issues/572
Nudges will frequently not show up when I visit facebook. Why is this? I haven't accidentally turned them off.

https://github.com/habitlab/habitlab/issues/571
Banner is too large

https://github.com/habitlab/habitlab/issues/570
the nudges arent really working....i have visited facebook multiple times now, but not have been nudged even once. I have enabled all the nudges as to see which one helps me the best, but its not nudging at all.

https://github.com/habitlab/habitlab/issues/569
None of the nudges are showing up. I'm not sure how to track down the issue.  I've pasted the contents of the javascript console from a visit to YouTube here https://pastebin.com/ZyPYB2Tw in case it helps track down the issue. Does HabitLab not work alongside adblockers or ghostery or something like that?

https://github.com/habitlab/habitlab/issues/568
Thanks

https://github.com/habitlab/habitlab/issues/567
your "how should we handle this" modal thing disappears on most pages before any human brain can be expected to click the options

https://github.com/habitlab/habitlab/issues/566
The extension doesn't track subdomains of a main domain properly. Suppose I add xyz.com as a filter and then it directs me to abc.xyz.com, the filter doesn't provide the needed nudges. This can be helpful if implemented.

https://github.com/habitlab/habitlab/issues/565
HabitLab extension in Chrome is using a lot of CPU

https://github.com/habitlab/habitlab/issues/564
Please add a login option at the start of the onboarding process to pull down any sync'ed data. I use a number of browsing logins on a number of computers and don't want to have to choose the list of sites every time. Also, a 'logout' option would be good. Also also, an email+password login would be handy for those who don't want to use a google account for this (or who want to share tracking and prefs across work and personal browser sessions)

https://github.com/habitlab/habitlab/issues/563
I believe settings across similar devices (laptop and desktop versus tablet and smartphone) should sync.

https://github.com/habitlab/habitlab/issues/562
I would love it if it would give me a running tally of my total minutes spent in addition to the "Today's five most visited sites by minutes spent" Thanks and cheers!

https://github.com/habitlab/habitlab/issues/561
How much time did I spend on what tabs, last week? Where are the totals?

https://github.com/habitlab/habitlab/issues/560
Think twice nudge for youtube does not work.

https://github.com/habitlab/habitlab/issues/558
How do I sign in to sync after the onboarding process? (Sign in to sync didn't work when I onboarded)

https://github.com/habitlab/habitlab/issues/557
Why do I not always receive a nudge when I visit facebook, I keep compulsively checking, and hoping a nudge will remind me, but I don't seem to be seeing any.

https://github.com/habitlab/habitlab/issues/554
I used two computers. On both computers, I am logged into Chrome with the same account as well as logged into HabitLab.  However, my settings are not in sync.

https://github.com/habitlab/habitlab/issues/553
Can you make a whitelist version?

https://github.com/habitlab/habitlab/issues/550
how about running it in incognito mode

https://github.com/habitlab/habitlab/issues/548
Please add a whitelist for stricter management, so we add the sites we DO want to access.

https://github.com/habitlab/habitlab/issues/547
Feed Eater Bug-  if I have the feed eater feature enabled, every time I open facebook, there will be an alert window along the lines of "How aggressive would you like HabitLab to be in helping you reduce your time spent this visit?", which gets tiring when you have to open facebook a lot of times for personal matters (not time wasting stuff I swear)

Update: Actually ignore what I just said about the Feed Eater bug, even with the feature off the issue continues on.

https://github.com/habitlab/habitlab/issues/546
Feed Eater Bug-  if I have the feed eater feature enabled, every time I open facebook, there will be an alert window along the lines of "How aggressive would you like HabitLab to be in helping you reduce your time spent this visit?", which gets tiring when you have to open facebook a lot of times for personal matters (not time wasting stuff I swear)

https://github.com/habitlab/habitlab/issues/545
Feed Eater  Bug

https://github.com/habitlab/habitlab/issues/544
Please let me have the "Mission Objective" nudge on youtube as well! I feel like it's one of the most effective nudges and would really make me consider twice whether to watch youtube or not.

https://github.com/habitlab/habitlab/issues/542
I have nudges/goals turned on, but they aren't appearing on any of the sites I enabled them on.

https://github.com/habitlab/habitlab/issues/538
Sidekicker, and NoComments are not working on YouTube.com. They work on "Try now" mode, but when actually expecting it to run while browsing, it does not work. I can see see Comments and Side bar.

https://github.com/habitlab/habitlab/issues/536
nudge "1 min assassin" that decreases to e.g. 30sec assasin if you already spent 10 minutes on the domain

https://github.com/habitlab/habitlab/issues/533
have multiple slots for work times. eg : 8h00 12h00 and 14h00 18h00

https://github.com/habitlab/habitlab/issues/530
In the selector for picking work days to be active it's very ambiguous which color means on and which means off.

https://github.com/habitlab/habitlab/issues/529
It seems like I can't add my own nudge idea because the "site which this nudge will be used on" dropdown is empty.

https://github.com/habitlab/habitlab/issues/527
Copy-pasted the js source for a built-in nudge into the editor and ran it. Had unexpected bugs not present in the built-in version.

Copy-pasted habitlab/src/interventions/youtube/remove_sidebar_links/frontend.js at commit da2cf17 into the nudge editor and ran it. All the comments as well as the tile of the video get grayed out, left menu no longer shows up when clicking the button (three paraller horizontal bars on the top left corner). This doesn't happen when running the built-in nudge. (Running Chrome. Youtube in dark-theme mode.)

Shouldn't they behave the same?

https://github.com/habitlab/habitlab/issues/522
I want to be able to temporarily turn off nudges for a particular website. For example, I'm watching educational youtube videos, but still want to avoid other sites.

https://github.com/habitlab/habitlab/issues/519
I've only been trying this out for about ~10 minutes and so far everything is working very well. I'm extremely pleased with it. However, I have different nudges enabled for different sites, but some sites are showing me nudges that should be disabled for that site. For example -- I have the more hardcore nudges like 1-min assasin and scroll blocker (cant remember specific name, sorry) turned on for both Instagram and Facebook, but only the ones like the timer/supervisor/objective nudges for Reddit. I use Reddit for work-related things often so I just need to be reminded to stay on task moreso than being blocked from the website altogether. I just opened reddit and the scroll-blocker nudge is what popped up even though it's specifically disabled for that site. Does HabitLab need to cycle through all the nudges once before it starts to show only enabled ones, or am I missing something? I can simply bypass the nudge but that defeats the purpose of enabling the other, more useful ones on this site. Thank you!

https://github.com/habitlab/habitlab/issues/517
When I turn off for the day/for the rest of the visit, it would be nice not to have a modal to confirm : I need one more click to close it, and it's annoying. If I wan't to turn it off, then there is no use anymore to slow down my use of thoses websites. See https://modalzmodalzmodalz.com/ for help

https://github.com/habitlab/habitlab/issues/516
Even when switching the Scroll Freeze off, the feature is applied. It freezes the scroll on websites that aren't even restricted.

https://github.com/habitlab/habitlab/issues/515
Intervention editor does not deploy nudges on "run this nudge" button

https://github.com/habitlab/habitlab/issues/514
Facebook nudges are not being deployed

https://github.com/habitlab/habitlab/issues/513
The Bouncer nudge shows the "how much time do you want to spend on this site" message too briefly for me to make a selection. Then it moves on to the site and closes it (because the default time setting is 0 minutes).

https://github.com/habitlab/habitlab/issues/512
Start making font (and other content) fade to grey with each scroll. Slowly the font will become tougher and tougher to read.

https://github.com/habitlab/habitlab/issues/511
This is one of the most useful extensions when it comes to fighting web addiction. However, many of the nudges, such as the news eater for Facebook fail to work at some occasions. And most of them does not work when combined with other nudges. This often defeats the purpose of the extension entirely. Otherwise, I love the idea of having nudges, the pie chart for an overview and setting daily limits. In the meantime however, I will use News Feed Eradicator for Facebook, WasteNoTime and RescueTime instead.

https://github.com/habitlab/habitlab/issues/508
I don't want to see the timer counting how long I've been on sites that I don't wish to spend less time on

https://github.com/habitlab/habitlab/issues/507
If I can disable the activated nudges easily, then there is no need for this extension. changing habits must be forced by rules made by the user.

https://github.com/habitlab/habitlab/issues/504
My settings are lost once I close Chrome.

https://github.com/habitlab/habitlab/issues/503
signed in to synch,  but after sign in synch  not implemented

https://github.com/habitlab/habitlab/issues/499
Hello, I really enjoyed using HabitLab, however I noticed it is consuming 16 -> 21% CPU, even when it is toggled 'Off' or otherwise not in use while on. This is unacceptable so it is being removed from my system (MacOS 10.13.6)

https://github.com/habitlab/habitlab/issues/498
XXXXXXXX

https://github.com/habitlab/habitlab/issues/497
I no longer see the pie chart with time spent on each site. How do I get that back?

https://github.com/habitlab/habitlab/issues/495
The piechart is not showing

https://github.com/habitlab/habitlab/issues/494
For some reason, graph doesn't show.

https://github.com/habitlab/habitlab/issues/492
there is something wrong ,the site isn't tracking my activities

https://github.com/habitlab/habitlab/issues/491
i can't see my most visited sites, it's not working

https://github.com/habitlab/habitlab/issues/490
I can't see the pie chart on the extension or the web page.

https://github.com/habitlab/habitlab/issues/488
i need the same software for firefox , how can i do ? can you help me ? and send me an email ?

https://github.com/habitlab/habitlab/issues/485
the extension for chrome(my verison is:Version 68.0.3440.106 (Official Build) (64-bit)) keeps hiding my you tube videos, it seems like a bug due to still keeping the names of the pages on the screen.

https://github.com/habitlab/habitlab/issues/482
Sometimes input messages don't work. The Mission Control nudge will display without asking for the objective (reading "Objective: " at the top), and the Bouncer will display without asking for the time, defaulting to zero minutes and immediately displaying the "Close tab / Turn off Bouncer / Cheat for 30 seconds" choice. Doesn't seem to have occurred on any of the default recommended sites, only on sites manually added by URL or the extension icon.

https://github.com/habitlab/habitlab/issues/480
Instead of Scroll Freezer I would just love a permanent feed remover! Let the feed be only as long as the window instead of infinite.

https://github.com/habitlab/habitlab/issues/472
I have an idea for a nudge. I would like to be able to remove "likes" from Instagram so that I don't see the number of "likes"  I receive--only that people liked it or did not.

https://github.com/habitlab/habitlab/issues/471
why does it show that i am spending time on facebook when my account has been suspended.

https://github.com/habitlab/habitlab/issues/470
I'm really excited about using this site but I did notice that the voting at the bottom of the habitlab chrome extension seems against the purpose of becoming less addicted to sites.  What's to stop people from constantly voting about the best nudges other than adding habitlab itself, if possible to do, to the list of sites to spend less time on? Just seems a bit contradictory.  I like the idea of asking for peoples' opinion but I'd say cap it at maybe 2 or 3 votes per time using the extension.

https://github.com/habitlab/habitlab/issues/469
"bouncer" doesn't work when you open internal links from within a blocked page (such as a facebook comment thread from your notifications, a reddit crosspost, etc). WOuld be great if it worked!

https://github.com/habitlab/habitlab/issues/468
There should be the ability to white list specific website to encourage certain behavior.

https://github.com/habitlab/habitlab/issues/466
Too many notifications interrupt my thought processes.  Hiding clickbait? I'm all for that.

https://github.com/habitlab/habitlab/issues/465
Show Stats from Yesterday (or more days from the past)

https://github.com/habitlab/habitlab/issues/464
not working on feedly.com -

https://github.com/habitlab/habitlab/issues/460
(from geza) font is off in the goal suggestion interface

https://github.com/habitlab/habitlab/issues/452
I don't see any option for easily changing over to purely tracking purposes - I have to manually turn off (permanently) each nudge AS IT  HAPPENS in order to do this, and since this doesn't integrate across instances of chrome (all my machines), I think I'm going to have to do this for each location that I use Chrome in.

https://github.com/habitlab/habitlab/issues/451
(from geza) css for the suggest goals interface seems to be off here compared to other sites. shadow dom issue? also the gitter api seems to have changed breaking our report bug functionality

https://github.com/habitlab/habitlab/issues/446
I turned the restrict your time nudge off because it caps at 5 min. I like the idea, but it needs to be free form.

https://github.com/habitlab/habitlab/issues/444
When given prompts for which nudges I think would be better, I got presented with two identical options - write some code that skips the comparison when that happens? (Also, the widening of this feedback rectangle while typing is a little disorienting; fixed-width would probably look nicer.)

https://github.com/habitlab/habitlab/issues/442
Please add a 1 hour or 2 hour disable for the interventions, "rest of today" produces unwanted results if I click it at (for example) 1AM, I want it to come back on after a while but not 24 whole hours

https://github.com/habitlab/habitlab/issues/438
Is there an option to block the site completely?

https://github.com/habitlab/habitlab/issues/437
I wish there was an option to set a goal and get pop-ups etc just for using Chrome at all, regardless of the site.

https://github.com/habitlab/habitlab/issues/436
Prompts if you would like to watch again or not when using the loop feature. Very annoying when playing music in the background.

https://github.com/habitlab/habitlab/issues/431
how about a metric that would total the time online from various sites and compare that against the aggregate "budget of time" for all sites?

https://github.com/habitlab/habitlab/issues/429
It would be great to have positive nudges as well. For example, a screen that asks if you would like to spend time on a site related to something one intends to do more of (meditation, exercise, job search)

https://github.com/habitlab/habitlab/issues/428
This app is not tracking my activity anymore

https://github.com/habitlab/habitlab/issues/427
I want to spend LESS time on the nytimes

https://github.com/habitlab/habitlab/issues/416
There was something to remind me to visit important sites ,, where is that feature ?

https://github.com/habitlab/habitlab/issues/415
(from geza) regression in youtube pause videos intervention

https://github.com/habitlab/habitlab/issues/411
I'm trying to set the hours nudges are active via "only work hours." It won't let me set them also for my sleep hours! I would like the nudges active from 11pm to 5pm

https://github.com/habitlab/habitlab/issues/406
YOU GUYS ARE AWESOME! I love nudges. I love Stanford. This helps me so much. I wish everybody knew about it.

https://github.com/habitlab/habitlab/issues/404
Guys, I fuckingly love what you made! I send you all my gratitude for your wonderful product!

https://github.com/habitlab/habitlab/issues/399
Settings aren't synced between browsers



I installed the extension on Chrome and customized some settings. When I opened Canary Chrome, the extension was installed, but the settings weren't synced. It's possible that this is a problem with Canary, but my guess is that settings also aren't synced between Google Chrome on different desktop machines.



The ideal solution would be to have user accounts, so that once the extension is available on other browsers, your settings could be synced between them. But it would probably be much easier to rely on Chrome's syncing for the time being, which would provide most of the benefit. (People probably tend to use the same browser on different devices.)



Keywords: sync, synch, synchronize, synchronization

https://github.com/habitlab/habitlab/issues/395
No increase in time though I often visit the page I want to reduce time on

https://github.com/habitlab/habitlab/issues/389
You're telling me that I spent no time on FB or Youtube, when I definitely did. I've not turned off HabitLab, so how does your measurement system work? Are there any other Chrome extensions it doesn't work alongside with?

https://github.com/habitlab/habitlab/issues/386
I use lots of PCs and MACs and would like to see my HabitLab a rather cross-device, Gmail-based account. Thanks a lot for the great work.

https://github.com/habitlab/habitlab/issues/385
turned on for twitter - minute watch distracting / annoying, so turned on (?) "supervisor", turned off minute watch.  It doesn't take.  It still annoys.  I'm about to simply turn off habit lab as a result.

https://github.com/habitlab/habitlab/issues/384
tiny bug, every midnight it shows a popup about having accomplished my goals of the starting day which obviously of course not the case

https://github.com/habitlab/habitlab/issues/381
I've had the extension installed for a few days now, but so far it hasn't tracked ANY minutes on ANY website. Happy to provide a list of current/active extensions if it would help. My first instinct is perhaps "HTTPS Everywhere"?

https://github.com/habitlab/habitlab/issues/380
Timer stops sometimes

https://github.com/habitlab/habitlab/issues/379
It does not accurately track the amount of time spent on Netflix, unless you are moving your mouse around. It starts counting, but then pauses counting after your mouse hasn't moved for a few minutes - i.e. passively watching a video. It was unable to accurately track the minutes spent even though the timer function was on, and I was interacting with it by pressing "snooze" a few times.

https://github.com/habitlab/habitlab/issues/377
As an alternate to a addictive site, you should let people completely step away and engage elsewhere. The alternative to a website should not only be another website.

https://github.com/habitlab/habitlab/issues/376
I hope this add-on works with Chrome on incognito windows as well!

https://github.com/habitlab/habitlab/issues/369
At times I am using youtube for educational content and would be nice to submit pages as educational so they dont trigger any HabitLabbehavior.

https://github.com/habitlab/habitlab/issues/363
It appears that the clock does not accurately count time spent on Netflix when in full-screen mode. It begins counting, but then pauses.

https://github.com/habitlab/habitlab/issues/362
I'm loving HabitLab so far. An additional suggestion: I want HabitLab to play a distinctive sound when a nudge is activated. Noises can be annoying, but they can also be a powerful part of retraining our habits. The user should obviously have the option to silence HabitLab, but the sound option would be a big upgrade. I would be glad to help develop a sound (or array of sounds) that could be used for this.

https://github.com/habitlab/habitlab/issues/361
Please allow option to not turn off buttons, e.g. "turn off feed eater button". Ideally this is a global option across all extensions. Thanks! :)

https://github.com/habitlab/habitlab/issues/348
There should be a way to combine sites into the same grouping (i.e. smile.amazon.com and www.amazon.com, and to account for different parts of the site, such as music vs. shopping)

\end{lstlisting}
